Implicit yaddayadda

### 2011-10-25 papers/PLDI2012/implicitization.tex
presentation du tableau

In this section, our experimental results come from the analysis of various
open-source projects listed in Figure \ref{fig:projects}, written in C, C++ and
Fortran.
\begin{figure}[!h]
	\centering
\begin{tabular}{|l|r|r|} \hline
	Name & LOC & $|P_R|$ \\ \hline
	a2ps & 55k & 2012\\
	gawk & 59k & 902\\ 
	gnuchess & 38k & 1222\\ 
	gnugo & 83k & 2801\\
	grep & 35k & 820\\
	gzip & 27k & 494\\
	lapack/blas & 954k & 16422\\
	make & 34k & 993\\ 
	sed & 23k & 292\\
	tar & 73k & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{|l||r|r|r||r|r|r||r|r|r||r|r|r||r|r|r||} \hline
\textbf{Benchmark} & \multicolumn{3}{c||}{\textbf{G/S}}
& \multicolumn{3}{c||}{\textbf{PF/S}}
& \multicolumn{3}{c||}{\textbf{PF/G}}
& \multicolumn{3}{c||}{\textbf{G+PF/PF}}
& \multicolumn{3}{c||}{\textbf{G+PF/G}} \\ \cline{2-16}
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} \\
 \hline
 \input{table1.tex}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focused} technique (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm. \textbf{lt} column gives the
percentage of invariants more precise with the left-side technique,
\textbf{gt} the percentage of invariants better with the right-side technique,
and \textbf{un} gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
\label{tab:techniques}
\end{table*}

>>>>

In this section, our experimental results come from the analysis of various
open-source projects listed in Figure \ref{fig:projects}, written in C, C++ and
Fortran.
\begin{figure}[!h]
	\centering
\begin{tabular}{|l|r|r|} \hline
	\multicolumn{1}{|c|}{Name} &
        \multicolumn{1}{c|}{kLOC} &
        \multicolumn{1}{c|}{$|P_R|$} \\ \hline
	a2ps & 55 & 2012\\
	gawk & 59 & 902\\ 
	gnuchess & 38 & 1222\\ 
	gnugo & 83 & 2801\\
	grep & 35 & 820\\
	gzip & 27 & 494\\
	lapack/blas & 954 & 16422\\
	make & 34 & 993\\ 
	sed & 23 & 292\\
	tar & 73 & 1712\\
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{|l|rrr|rrr|rrr|rrr|rrr|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & inc.
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & inc.
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & inc.
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & inc.
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & inc. \\
 \hline
 \input{table1.tex}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focused} technique (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subseteq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\subseteq$ the percentage of invariants better with the right-side technique,
and ``inc.'' gives the percentage of invariants that are incomparable, i.e
neither greater nor smaller.}
% TODO: le reste c'est quand c'est egal?
\label{tab:techniques}
\end{table*}
